---
title: "Homework #2"
author: "Michael Costello"
format: html
editor: visual
---


#Task 1: Basic Vector Practice

1. Create two vectors of the pre- and post-measurements:

```{r}
pre <- c(130, 128, 116, 124, 133, 134, 118, 126, 114, 127, 141, 138, 128, 140, 137, 131, 120, 128, 139, 135)

post <- c(114, 98, 113, 99, 107, 116, 113, 111, 119, 117, 101, 119, 130, 122, 106, 106, 124, 102, 117, 113)
```

2. Assign names to the vector elements:

```{r}
names(pre)  <- paste("Subject", 1:20, sep = "_")
names(post) <- paste("Subject", 1:20, sep = "_")
```

3. Calculate the change (decrease?) in blood pressure accross all patients:

```{r}
diff <- pre - post
diff
```
4. Find the average decrease in BP across all patients:

```{r}
mean(diff)
```
5. Patients who experienced a deceased in BP after treatment:

```{r}
improved <- which(diff > 0, useNames = TRUE)
improved
```

6. Create a new vector object with only improvers and their BPs:

```{r}
improved <- which(diff > 0)  #Well, this is incorrect. I can't figure out how to get just the BPs rather than their indices.
improved
```

7. Find the mean of the improvers BPs:

```{r}
mean(improved)
```

